---
title             : "A practical primer on processing semantic property norm data"
shorttitle        : "Processing Norms"

author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
  - name          : "Simon De Deyne"
    affiliation   : "2"
  - name          : "Maria Montefinese"
    affiliation   : "3"    

affiliation:
  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Melbourne"
  - id            : "3"
    institution   : "University of Padua"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Semantic property listing tasks require participants to generate short propositions (e.g., <barks>, <has fur>) for a specific concept (e.g., dog). This task is the cornerstone of the creation of semantic property norms which are essential for modelling, stimuli creation, and understanding similarity between concepts. However, despite the wide applicability of semantic property norms for a large variety of concepts across different groups of people, the methodological aspects of the property listing task have received less attention, even though the procedure and processing of the data can substantially affect the nature and quality of the measures derived from them. The goal of this paper is to provide a practical primer on how to collect and process semantic property norms. We will discuss the key methods to elicit semantic properties and compare different methods to derive meaningful representations from them.  This will cover the role of instructions and test context, property pre-processing (e.g., lemmatization), property weighting, and relationship encoding using ontologies. With these choices in mind, we propose and demonstrate a processing pipeline that transparently documents these steps resulting in improved comparability across different studies. The impact of these choices will be demonstrated using intrinsic (e.g. reliability, number of properties) and extrinsic measures (e.g., categorization, semantic similarity, lexical processing). Example data and the impact of choice decisions will be provided. This practical primer will offer potential solutions to several longstanding problems and allow researchers to develop new property listing norms overcoming the constraints of previous studies.
  
keywords          : "semantic, property norm task, tutorial"

#bibliography      : ["r-references.bib"] add this later

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

1.	Available feature norms and their format

- Property listing task original work: @Toglia1978; @Toglia2009; @Rosch1975; @Ashcraft1978a 
- English: @McRae2005, @Vinson2008, @Buchanan2013, @Devereux2014, @Buchanan2019
- Italian: @Montefinese2013; @Reverberi2004, @Kremer2011a
- German: @Kremer2011a
- Portuguese: @Stein2009
- Spanish: @Vivas2017
- Dutch: @Ruts2004
- Blind participants: @Lenci2013

I'm sure there are more, here's what we cited recently 

2.	Pointers about how to collect the data
a.	instructions, generation, verification, importance

I really like the way the CSLB did it: https://cslb.psychol.cam.ac.uk/propnorms

They showed the concept, then had a drop down menu for is/has/does, and then the participant typed in a final window. That type of system would solve about half the problems I am going to describe below about using multi-word sequences. Might be some other suggestions, but for that type of processing, you could do combinations and have more consistent data easily. 

3.	Typical operations performed on features



a.	stemming, spelling, normalization
i.	exceptions dictionary 
ii.	bing spell checker service
b.	Weighting 
c.	feature type ontologies
d.	identify cut off for idiosyncratic features (should it be necessary?) 
4.	Specification of how this is automated (package description)
a.	tests to see if things work: e.g. manual spell checks vs automated ones
5.	Evaluation of the approach
a.	internal (quality, size, consistency) - ? 
i.	feature size number of features work 
ii.	classifier for ontology, compare results to previous work 
b.	externally (categorization, similarity) – MEN dataset, Lapata categorization task 
6.	Challenges and opportunities


# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
